Supplementary Material: Constructing Statistical Deformable Models with Shape Flow

### 2015-04-29 supplementary.tex
Updates from ShareLaTeX

%%%%%%%%% TITLE
\title{Supplementary Materials: Constructing Statistical Deformable Models with Shape Flow}

@@

The supplementary materials provided detailed evaluation of dense Active Appearance Models (dAAMs) built with proposed pipeline of constructing dense AAMs without consistent set of landmarks. There are four experiments reported to support applications of dAAMs. Experiment \ref{sec:fittingresults} exhibits a full fitting visualisations of non-rigid face and ear alignment in-the-wild between classic AAMs and our dense AAMs. Experiments \ref{sec:modelanalysis} compares analytical qualities of our dAAMs with respect to that of classic aams in terms of model compactness, warping quality and reconstruction.
Moreover, experiment \ref{sec:reconstruct} serves as a qualitative demonstration of how the proposed pipeline can use be effectively used to generate novel modified instances of an object, e.g. caricatures, from simple hand drawn sketches.
Finally, experiment \ref{sec:segmentation} evaluates the effectiveness and performance of the proposed methodology to build dense AAMs of objects that are difficult to annotated with respect to a consistent set of landmarks, such as bottles and human bodies. Corresponding demonstration shows the usage of utilising dAAMs for objects segmentation.

%%%%%%%%% Appendix
\appendix
\section{Fitting Results}
\label{sec:fittingresults}

>>>>

%%%%%%%%% TITLE
\title{Supplementary Material: Constructing Statistical Deformable Models with Shape Flow}

@@

%%%%%%%%% Appendix
\appendix
\section{Introduction}
In this supplementary material, we provide additional experimental results and comparisons for the proposed pipeline of constructing dense AAMs without consistent set of landmarks. 
We present four different sets of experiments.

reported to support applications of dAAMs.

In Section \ref{sec:fittingresults}, we present visualisations of in-the-wild model fitting  for faces and ears, comparing classic AAMs and the proposed dense AAMs. In Section \ref{sec:modelanalysis}, we compares analytical qualities of our dAAMs with respect to that of classic aams in terms of model compactness, warping quality and reconstruction.
Moreover, experiment \ref{sec:reconstruct} serves as a qualitative demonstration of how the proposed pipeline can use be effectively used to generate novel modified instances of an object, e.g. caricatures, from simple hand drawn sketches.
Finally, experiment \ref{sec:segmentation} evaluates the effectiveness and performance of the proposed methodology to build dense AAMs of objects that are difficult to annotated with respect to a consistent set of landmarks, such as bottles and human bodies. Corresponding demonstration shows the usage of utilising dAAMs for objects segmentation.

\section{Fitting Results}
\label{sec:fittingresults}
